The guts of the dispRity package

### 2017-11-15 inst/gitbook/03_specific-tutorials.Rmd
Updated manual

 *  `acctran` where the data chosen along the branch is always the one of the descendant
 *  `deltran` where the data chosen along the branch is always the one of the ancestor
 *  `punctuated` where the data chosen along the branch is randomly chosen between the descendant or the ancestor
 *  `gradual` where the data chosen along the branch is either the descendant or the ancestor depending on branch length

```{r, eval=TRUE}
## Generating four time slices every 40 million years under a model of gradual evolution
time.subsamples(data = BeckLee_mat99, tree = BeckLee_tree, 
    method = "continuous", model = "gradual", time = c(120, 80, 40, 0),
    FADLAD = BeckLee_ages)

## Generating four time slices automatically
time.subsamples(data = BeckLee_mat99, tree = BeckLee_tree,
    method = "continuous", model = "gradual", time = 4, FADLAD = BeckLee_ages)
```

@@

## Creating time slice subsamples
time_slices <- time.subsamples(data = BeckLee_mat99, tree = BeckLee_tree, 
                               method = "continuous", model = "gradual", 
                               time = c(120, 80, 40, 0),
                               FADLAD = BeckLee_ages)

@@

## Creating time slice subsamples
time_slices <- time.subsamples(data = BeckLee_mat99, tree = BeckLee_tree, 
    method = "continuous", model = "gradual", time = c(120, 80, 40, 0),
    FADLAD = BeckLee_ages)
## Bootstrapping the time slice subsamples
boot_time_slices <- boot.matrix(time_slices, bootstraps = 100)
## Calculate disparity
disparity_time_slices <- dispRity(boot_time_slices, metric = c(sum, variances))

>>>>

 *  `acctran` where the data chosen along the branch is always the one of the descendant
 *  `deltran` where the data chosen along the branch is always the one of the ancestor
 *  `random` where the data chosen along the branch is randomly chosen between the descendant or the ancestor
 *  `proximity` where the data chosen along the branch is either the descendant or the ancestor depending on branch length
 *  `punctuated` where the data chosen along the branch is both the descendant and the ancestor with an even probability
 *  `gradual` where the data chosen along the branch is both the descendant and the ancestor with a probability depending on branch length

> Note that the four first models are "fixed": the selected data is always either the one of the descendant or the ancestor.
The two last models are "probabilistic": the data from both the descendant and the ancestor is used with an associate probability.
These later models perform better when bootstrapped, effectively approximating the "intermediate" state between and the ancestor and the descendants.

```{r, eval=TRUE}
## Generating four time slices every 40 million years under a model of proximity evolution
time.subsamples(data = BeckLee_mat99, tree = BeckLee_tree, 
    method = "continuous", model = "proximity", time = c(120, 80, 40, 0),
    FADLAD = BeckLee_ages)

## Generating four time slices automatically
time.subsamples(data = BeckLee_mat99, tree = BeckLee_tree,
    method = "continuous", model = "proximity", time = 4, FADLAD = BeckLee_ages)
```

@@

## Creating time slice subsamples
time_slices <- time.subsamples(data = BeckLee_mat99, tree = BeckLee_tree, 
                               method = "continuous", model = "proximity", 
                               time = c(120, 80, 40, 0),
                               FADLAD = BeckLee_ages)

@@

## Creating time slice subsamples
time_slices <- time.subsamples(data = BeckLee_mat99, tree = BeckLee_tree, 
    method = "continuous", model = "proximity", time = c(120, 80, 40, 0),
    FADLAD = BeckLee_ages)
## Bootstrapping the time slice subsamples
boot_time_slices <- boot.matrix(time_slices, bootstraps = 100)
## Calculate disparity
disparity_time_slices <- dispRity(boot_time_slices, metric = c(sum, variances))

### 2017-11-15 inst/gitbook/05_guts.Rmd
Updated manual

 * `$call$subsamples`: a vector of `character` with information on the subsamples type (either `"continuous"`, `"discrete"` or `"custom"`) and their eventual model (`"acctran"`, `"deltran"`, `"punctuated"`, `"gradual"`). This element generated only once via `time.subsamples()` and `custom.subsamples()`.
 * `$call$dimensions`: either a single `numeric` value indicating how many dimensions to use or a vector of `numeric` values indicating which specific dimensions to use. This element is by default the number of columns in `$matrix` but can be modified through `boot.matrix()` or `dispRity()`.
 * `$call$bootstrap`: this is a `list` containing three elements:
    * `[[1]]`: the number of bootstrap replicates (`numeric`)
    * `[[2]]`: the bootstrap method (`character`)
    * `[[3]]`: the rarefaction levels (`numeric` vector)
 * `$call$disparity`: this is a `list` containing one element, `$metric`, that is a `list` containing the different functions passed to the `metric` argument in `dispRity`. These are `call` elements and get modified each time the `dispRity` function is used (the first element is the first metric(s), the second, the second metric(s), etc.).

>>>>

 * `$call$subsamples`: a vector of `character` with information on the subsamples type (either `"continuous"`, `"discrete"` or `"custom"`) and their eventual model (`"acctran"`, `"deltran"`, `"random"`, `"proximity"`, `"punctuated"`, `"gradual"`). This element generated only once via `time.subsamples()` and `custom.subsamples()`.
 * `$call$dimensions`: either a single `numeric` value indicating how many dimensions to use or a vector of `numeric` values indicating which specific dimensions to use. This element is by default the number of columns in `$matrix` but can be modified through `boot.matrix()` or `dispRity()`.
 * `$call$bootstrap`: this is a `list` containing three elements:
    * `[[1]]`: the number of bootstrap replicates (`numeric`)
    * `[[2]]`: the bootstrap method (`character`)
    * `[[3]]`: the rarefaction levels (`numeric` vector)
 * `$call$disparity`: this is a `list` containing one element, `$metric`, that is a `list` containing the different functions passed to the `metric` argument in `dispRity`. These are `call` elements and get modified each time the `dispRity` function is used (the first element is the first metric(s), the second, the second metric(s), etc.).
